### 2017-05-06 2017mergingmerges/section/05-Evaluation.tex
Cut back optimisation and proof sections to save space

Another optimization is to notice that in some cases, when a heap variable is updated it is always assigned the value of another variable. In Fig.~\ref{fig:Process:Fused}, the @v@ and @x1@ variables are only ever assigned the value of @b1@, and @b1@ itself is only ever loaded via a @pull@ instruction. Remember from \S\ref{s:Fusion:FusingPulls} that the variable @b1@ is the stream buffer variable. Values pulled from stream @sIn1@ are first stored in @b1@ before being copied to @v@ and @x1@. When the two processes to be fused share a common input stream, use of stream buffer variable allows one process to continue using the value that was last pulled from the stream, while the other moves onto the next one.

When the two processes are able to accept the next variable from the stream at the same time, there is no need for the separate stream buffer variable. This is the case in Fig.~\ref{fig:Process:Fused}, and we can perform a copy-propagation optimisation, replacing all occurrences of @v@ and @x1@ with the single variable @b1@. In the result, the interleaved instructions from both source processes then share the same heap variable.

To increase the chance that we can perform this above copy-propagation, we need both processess to want to pull from the same stream at the same time. In the definition of a particular process, moving the @drop@ instruction for a particular stream as late as possible prevents a @pull@ instruction from a second process being scheduled in too early. In general, the @drop@ for a particlar stream should be placed just before a @pull@ from the same stream.

>>>>

% Another optimization is to notice that in some cases, when a heap variable is updated it is always assigned the value of another variable. In Fig.~\ref{fig:Process:Fused}, the @v@ and @x1@ variables are only ever assigned the value of @b1@, and @b1@ itself is only ever loaded via a @pull@ instruction. Remember from \S\ref{s:Fusion:FusingPulls} that the variable @b1@ is the stream buffer variable. Values pulled from stream @sIn1@ are first stored in @b1@ before being copied to @v@ and @x1@. When the two processes to be fused share a common input stream, use of stream buffer variable allows one process to continue using the value that was last pulled from the stream, while the other moves onto the next one.

When the two processes are able to accept the next variable from the stream at the same time, there is no need for the separate stream buffer variable. This is the case in Fig.~\ref{fig:Process:Fused}, and we can perform a copy-propagation optimisation, replacing all occurrences of @v@ and @x1@ with the single variable @b1@. To increase the chance that we can perform copy-propagation, we need both processess to want to pull from the same stream at the same time. Moving the @drop@ instruction for a particular stream as late as possible prevents a @pull@ instruction from a second process being scheduled in too early.

% In the result, the interleaved instructions from both source processes then share the same heap variable.

% In general, the @drop@ for a particlar stream should be placed just before a @pull@ from the same stream.

### 2017-05-06 2017mergingmerges/section/XX-Proof.tex
Cut back optimisation and proof sections to save space

The @Soundness@ theorem uses @EvalBs@ to evaluate the fused program, and @EvalOriginal@ ensures that the original program evaluates with that program's subset of the result heap, using @Var1@ and @Var2@ to extract the variables.

@@

To aid mechanization, the Coq formalization has some small differences from the system presented in this paper. Instead of implementing non-deterministic evaluation we sequentially evaluate each source processes independently, and compare the output values to the ones produced by sequential evaluation of the fused result process. This is sufficient for our purposes because we are mainly interested in the value correctness of the fused program, rather than making a statement about the possible execution orders of the source processes when run concurrently.

>>>>

@EvalBs@ evaluates the fused program, and @EvalOriginal@ ensures that the original program evaluates with that program's subset of the result heap. The Coq formalization has some small differences from the system in this paper. Instead of implementing non-deterministic evaluation we sequentially evaluate each source processes independently, and compare the output values to the ones produced by sequential evaluation of the fused result process. This is sufficient for our purposes because we are mainly interested in the value correctness of the fused program, rather than making a statement about the possible execution orders of the source processes when run concurrently.

@@
